%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
      {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Ryan Qin} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 647-970-8858~ \href{l29qin@uwaterloo.ca}{\raisebox{-0.2\height}\faEnvelope\  \underline{l29qin@uwaterloo.ca}} ~ 
    \href{https://www.linkedin.com/in/ryan-qin-4b8157130}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/lang98}{\raisebox{-0.2\height}\faGithub\ \underline{Github}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{}
      {Bachelor of Applied Science in Computer Engineering, option in Artificial Intelligence}{Waterloo, ON, Canada}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: TypeScript, Java, Python, Ruby, Rust, C/C++, Kotlin, Go, Dart} \\
      \textbf{Developer Tools}{: React, Django, AWS, Terraform CDK, Ruby on Rails, CI/CD, Node, Docker, K8s, GraphQL} \\
    }}
  \end{itemize}
\vspace{-16pt}

%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     \begin{multicols}{4}
%         \begin{itemize}[itemsep=-5pt, parsep=3pt]
%             \item\small Data Structures
%             \item Software Methodology
%             \item Algorithms Analysis
%             \item Database Management
%             \item Artificial Intelligence
%             \item Internet Technology
%             \item Systems Programming
%             \item Computer Architecture
%         \end{itemize}
%     \end{multicols}
%     \vspace*{2.0\multicolsep}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon}{August 2022 -- Now}
      {Software Engineer}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Worked under Amazon Fintech to build a modern, highly scalable, multi-region payment transmission service; used technologies such as AWS, Java, Python, AWS CDK in TypeScript, and other internal tools.}
        \resumeItem{Implemented a feature to support disbursing payments in bulk through asynchronous workflows end to end, improving usability of the application.}
        \resumeItem{Investigated and root caused numerous latency spikes, error/fault alarms as service scales; worked with upstream teams and documented the required procedures to reduce them.}
      \resumeItemListEnd

    \resumeSubheading
      {Arund}{June 2022 -- Now}
      {Co-founder \& CTO}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{CTO, co-founder, creator of Arund - an online marketplace for advertisement.}
        \resumeItem{Developed and maintained the official website \href{https://arund.ca}{\underline{arund.ca}}, the mobile application available for iOS and Android, and the application server hosted on AWS; used React, Redux, React Native, Django, Terraform CDK.}
      \resumeItemListEnd

    \resumeSubheading
      {Cisco Meraki}{September 2020 -- August 2022}
      {Software Engineer}{Remote}
      \resumeItemListStart
        \resumeItem{Main developer of the Meraki Vision app \href{https://vision.meraki.com}{\underline{meraki.vision}} built with React, Redux, Ruby on Rails, used by millons of Meraki customers.}
        \resumeItem{Built the video streaming component using HLS, Three.js; improved the streaming performance by tweaking HLS configuration according to the type of camera hardware.}
        \resumeItem{Implemented end-to-end a search feature for different database models, imroving the software usability by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {TobyX}{January 2018 -- July 2020}
      {Technical Lead}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Lead the development of a museum exhibition app built with GraphQL and MongoDB; a social network app involving friending and posts; built with React Native, Redux, Express.}
        \resumeItem{Hosted weekly development scrum meetings and assign tickets to team members strategically.}
        \resumeItem{Configured application hosting with AWS using services such as S3, EC2, RDS and load balencer, ensured application availability accross multiple regions.}
      \resumeItemListEnd

    \resumeSubheading
      {Splunk}{September 2019 -- December 2019}
      {Frontend Developer Intern}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Implemented a CLI feature for Splunk Phantom, which provides hint-suggestion and auto-completion when typing in slash-commands; well received in the Phantom team demo and released to production.}
        \resumeItem{Actively seeking for improvement to achieve highest code quality possible, clearly documented using Confluence and JS docstring.}
      \resumeItemListEnd

    \resumeSubheading
      {Zynga}{January 2019 -- April 2019}
      {Mobile Game Developer Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Migrated the Words with Friends mobile game to React Native, MobX and Inversify. Created bridge functions in Java and Objective-C to allow native code execution in Javascript.}
        \resumeItem{Researched and worked on features involving third-party SDKs such as Facebook and Branch referral system to help increase user retention.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Sudoku solver} $|$ \emph{Rust}}{February 2021}
      \resumeItemListStart
        \resumeItem{Implemented multi-threading on top of a brute-force Sudoku solver to improve the performance, using Rust Mutex and threads.}
        \resumeItem{The result is checked against an online API to ensure the correctness of the algorithm.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%             \resumeItemListStart
%                 \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                 \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                 \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}
